Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-21 main.tex
Update on Overleaf.

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
% \usepackage{fullpage}
\input{header}

@@

% DONE: MV : Be more didactical: write following as the existence of a potential. 
Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:intro:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
The different scalar potentials only differ by a constant. 
Therefore, %when the domain is connected, then 
this inequality is equivalent to the following statement: 
\begin{align}\label{math:intro:poincarefriedrichs:grad}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    \forall
    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
    .\tag{PF} 
\end{align}
% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
% \begin{align}\label{math:intro:poincarefriedrichs:grad}
%     \min\limits_{c\in\bbR}
%     \| u - c \|_{L^{p}(\Omega)}
%     \leq 
%     C_{\grad,\Omega,p} \| \nabla u \|_{L^p(\Omega)},
%     \quad 
%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
%     .\tag{PF} 
% \end{align}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
One example for a bounded linear operator is the average-free potential:
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*} 
Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
\begin{align}\label{math:intro:poincare:grad}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    , \tag{P} % DONE: tag Poincar\'e inequality 
\end{align}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.

@@

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{L^{p}(\Omega)}
    &\leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \\%\qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{L^{p}(\Omega)}
    &\leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and how these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \\
    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these points the \emph{vertices} of the simplex $T$. 
If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
then we call $S$ a \textit{subsimplex} of $T$ and we call $T$ a \textit{supersimplex} of $S$.

@@

Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields. 
We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.

@@

Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:

@@

    u \in L^p(\Omega)

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
    \leq 
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^p(\Omega)} }{ \| \nabla u \|_{L^p(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
\\

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\end{center}
\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.}
\label{figure:exhausting}
\end{figure}

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,p}
        &\leq 
        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
        \\
        %\quad 
        C_{{\rm PF},T,F,p}
        &\leq
        \frac{1}{\sqrt[p]{p}}
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \begin{gather*}
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
        .
    \end{gather*}
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \begin{gather*}
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \end{gather*}
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
        %\diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

@@

    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x)

@@

\begin{lemma}\label{lemma:oppositesubsimplex}
    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
    Then $T$ lies on one side of the affine subspace
    \begin{gather*}
        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
    \end{gather*}
    Moreover, $F = T \cap A$.
\end{lemma}
\begin{proof}
    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
    Let us now suppose that $x \in A \cap T$.
    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
    \begin{align}
        x &= 
        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
        \\&
        = 
        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
        + 
        \sum_{i=1  }^{k  } \lambda_{i} v_i 
        + 
        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
        + 
        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
        .
    \end{align}
    We know $x$ can be written as a unique convex combination of the vertices of $T$.
    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive. 
    If $x \notin F$, then at least one of these coefficients must be negative. 
    But then their sum must be negative, which is a contradiction. 
    The desired statement follows.         
\end{proof}

@@

    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{?}(T)$.
    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
    so that $\hat u \in \cartan \bfW^{p}\Lambda^{?}(\Delta^{n})$ and $\cartan \hat u = \hat f$.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
% \usepackage{fullpage}
\input{header}

@@

% DONE: MV : Be more didactical: write following as the existence of a potential. 
Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:intro:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
The different scalar potentials only differ by a constant. 
Therefore, %when the domain is connected, then 
this inequality is equivalent to the following statement: 
\begin{align}\label{math:intro:poincarefriedrichs:grad}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall
    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
    .\tag{PF} 
\end{align}
% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
% \begin{align}\label{math:intro:poincarefriedrichs:grad}
%     \min\limits_{c\in\bbR}
%     \| u - c \|_{L^{p}(\Omega)}
%     \leq 
%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
%     \quad 
%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
%     .\tag{PF} 
% \end{align}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
One example for a bounded linear operator is the average-free potential:
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*} 
Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
\begin{align}\label{math:intro:poincare:grad}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    , \tag{P} % DONE: tag Poincar\'e inequality 
\end{align}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.

@@

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \curl \bfu \in \bfL^{p}(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^{p}(\Omega) : \divergence \bfu \in L^{p}(\Omega) \right\}
    .
\end{align*}
Their members are those vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{L^{p}(\Omega)}
    &\leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \\%\qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{L^{p}(\Omega)}
    &\leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and how these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    &\Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \\
    &\Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these points the \emph{vertices} of the simplex $T$. 
If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
then we call $S$ a \textit{subsimplex} of $T$ and call $T$ a \textit{supersimplex} of $S$.

@@

Let us assume that $\Omega \subseteq \bbR^{n}$ is an open connected set. 
Given any $p \in [1,\infty]$, we let $L^{p}(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields. 
We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.

@@

Stern's generalized projection estimate~\cite[Theorem~4.1,Remark~5.1]{stern2015banach} implies improved estimate for all $L^{p}$ spaces with $1 \leq p \leq \infty$:

@@

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^{p}(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    \leq 
    \max\limits_{ u \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{{\rm P},\Omega,p}$.
\\

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!50] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=white  ] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!50] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=white  ] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!50] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=white  ] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\quad
\begin{tikzpicture}
    \coordinate (A) at (0,0);   \coordinate (B) at (2,0); \coordinate (C) at (1,1.5);
    \coordinate (D) at (0,2.9); \coordinate (E) at (2.5,3); \coordinate (F) at (3,1.25); 
    \draw[fill=gray!25] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!25] (A) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!25] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=gray!50] (B) -- (C) -- (F) -- cycle; 
\end{tikzpicture}
\end{center}
\caption{Exhausting a domain step by step as in Theorem~\ref{theorem:poincarefriedrichsestimate:grad} and \ref{theorem:poincarefriedrichsestimate:gradzwei}.
The dark gray triangle is the one being currently added, and the light gray triangles constitute the subdomain assembled so far.}
\label{figure:exhausting}
\end{figure}

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \| \nabla u \|_{L^{p}(T)}
        ,
    \end{align*}
    where $C_{{\rm PF},T,F,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,p}
        &\leq 
        C_{{\rm PF},T,p} + \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right)^{\frac 1 p},  
        \\
        %\quad 
        C_{{\rm PF},T,F,p}
        &\leq
        \frac{1}{\sqrt[p]{p}}
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \begin{gather*}
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{L^{p}(T)} % DONE: bold face or no boldface? No bold face 
        .
    \end{gather*}
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \begin{gather*}
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \end{gather*}
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        \\&
        \leq 
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \left( C_{{\rm PF},T,p}^{p} + p \cdot \diam(T) C_{{\rm PF},T,p}^{p-1} \right) 
        %\diam(T)^{p}
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

@@

    u(x) = \cartan \Poinc_{\ell} u(x) + \Poinc_{\ell+1} \cartan u(x).

@@

\begin{lemma}\label{lemma:oppositesubsimplex}
    Let $v_0, v_1, \dots, v_n \in \bbR^n$ be the vertices of a simplex $T$.
    Let $F, F'$ be the two subsimplices of $T$ with respective sets of vertices $v_0,\dots,v_k$ and $v_{k+1},\dots,v_n$.
    Then $T$ lies on one side of the affine subspace
    \begin{gather*}
        A := v_0 + \operatorname{lin}\{ v_1 - v_0, \dots, v_k - v_0 \} +  \operatorname{lin}\{ v_n - v_{k+1}, \dots, v_n - v_{n-1} \}.
    \end{gather*}
    Moreover, $F = T \cap A$.
\end{lemma}
\begin{proof}
    Evidently, $A$ has dimension $n-1$ and $F \cap A \cap T$.
    Let us now suppose that $x \in A \cap T$.
    For some real coefficients $\lambda_1,\dots,\lambda_{n-1} \in \bbR$, it holds that 
    \begin{align*}
        x &= 
        v_0 + \sum_{i=1}^{k} \lambda_{i} ( v_i - v_0 ) + \sum_{i=k+1}^{n-1} \lambda_{i} ( v_n - v_i )
        \\&
        = 
        \left( 1 - \sum_{i=1}^{k} \lambda_{i} \right) v_0 
        + 
        \sum_{i=1  }^{k  } \lambda_{i} v_i 
        + 
        \left( \sum_{i=k+1}^{n-1} \lambda_{i} \right) v_n
        + 
        \sum_{i=k+1}^{n-1} (-\lambda_{i}) v_i 
        .
    \end{align*}
    We know $x$ can be written as a unique convex combination of the vertices of $T$.
    Hence the $\lambda_{k+1}, \dots, \lambda_{n-1}$ are non-positive. 
    If $x \notin F$, then at least one of these coefficients must be negative. 
    But then their sum must be negative, which is a contradiction. 
    The desired statement follows.         
\end{proof}

@@

    Let $f = \cartan u$ with $u \in \bfW^{p}\Lambda^{k}(T)$.
    We set $\hat f := \varphi^{\ast} f$ and $\hat u = \varphi^{\ast} u$, 
    so that $\hat u \in \cartan \bfW^{p}\Lambda^{k}(\Delta^{n})$ and $\cartan \hat u = \hat f$.
